\documentclass{article}
\usepackage{fullpage}
\title{Oven-Fried Chicken Thighs with Buttermilk-Mustard Sauce}
\author{Chris Hayward}

\begin{document}
\maketitle

\section{Description:}
Breaded, honey mustard flavored chicken thighs that are crispy as a result of baking, providing a healthier alternative over frying.

\noindent Preheating the baking sheet helps to crisp the chicken on the bottom.

\section{Ingredients:}
\begin{itemize}
\item$\frac{1}{4}$ cup low-fat buttermilk
\item 4 teaspoons Dijon mustard
\item 1 tablespoon honey
\item$\frac{1}{4}$ teaspoon salt
\item$\frac{1}{4}$ teaspoon freshly ground black pepper
\item$\frac{1}{2}$ teaspoon dried rosemary
\item$\frac{1}{4}$ cup dry breadcrumbs
\item 2 tablespoons grated fresh Parmesan cheese
\item 4 (6-ounce) chicken thighs, skinned
\item cooking spray
\end{itemize}

\section{Steps:}
\begin{enumerate}
\item Preheat oven to 425
\item Combine first 6 ingredients in a small microwave-safe bowl.
\item Spoon 3 tablespoons buttermilk mixture into a shallow bowl.
\item Reserve remaining mixture.
\item Combine breadcrumbs and Parmesan cheese in a small bowl.
\item Dip chicken in 3 tablespoons buttermilk mixture.
\item Dredge chicken in breadcrumb mixture.
\item Chill 15 minutes.
\item Lightly coat a baking sheet with cooking spray and place in oven 5 minutes.
\item Place chicken on baking sheet.
\item Bake at 425 for 24 minutes or until a meat thermometer registers 180, turning chicken after 12 minutes.
\item Microwave reserved buttermilk mixture on HIGH for 20 seconds or until warm.
\item Drizzle sauce over chicken.
\end{enumerate}

Yield: 2 servings (serving size: 2 thighs and 2 tablespoons sauce).
\end{document}
